---
title: "Problem Set 6"
author: "Westley Cook"
date: "3/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# standard first load

library(tidyverse)

# loading for tables in question 1

library(gt)

# loading to use assignment pipe operator

library(magrittr)

# loading to use rep_sample_n for 1e

library(infer)

```

## Question 1: Sampling and Confidence Intervals

```{r question_1_setup, echo=FALSE}

# This r chunk writes two functions, one to create a deck of cards and another
# to draw n cards from that deck and report the cards' suit, value, points, or
# name.

# I wasn't sure at first if I could combine numerics and characters into the
# same column (for values), but it appears I can - and even better, looking at
# the resulting tibble reveals that all values in the value column have been
# automatically coerced into characters. Using c() and rep() to fill the points
# and suit columns was pretty straightforward. It was my first time using
# paste() but it was pretty easy to pick up.

create_deck <- function(){
tibble(value = c(rep(c(2:10, "J", "Q", "K", "A"), 4)),
       points = rep(c(2:10, rep(10, 4)), 4),
       suit = c(rep("diamonds", 13),
                rep("hearts", 13),
                rep("clubs", 13),
                rep("spades", 13)),
       name = paste(value, suit, sep = " of "))
}

# Set the possible values of the report parameter in this function to make it
# easier to use; added stopifnot() to throw an error if a non-numeric n value is
# input. After that, it was straightforward: make the deck, pull the column I
# want to see, and sample n cards from that column.

draw_card <- function(n, report = c("suit", "value", "points", "name")){
  stopifnot(is.numeric(n))
  create_deck() %>% 
  pull(report) %>% 
  sample(n)
}

```

#### 1a)

A call of my draw_card() function with n = 4 and report = "name" produces the following output:

```{r question_1a, echo=FALSE}

# This r chunk sets the seed to 2 (to standardize the random draw) and uses the
# draw_card() function to pull 4 cards and report their name; the output is
# printed directly into the HTML document, sans formatting, because the question
# prompt just asked for us to "print a call" to the function, and the 6a version
# of the pset shows an output box like the one this generates

set.seed(2)
draw_card(4, report = "name")

```

#### 1b)

```{r question_1b, echo=FALSE}

# This r chunk sets the seed to 3, creates a tibble of 5-card draws with a
# column to show whether those draws contain face cards, and prints the first 5
# rows of that tibble in a nice gt table

set.seed(3)

# Use map() and rep() to pass the value 5 into draw_card 100 times, saving the 5
# drawn cards as a list column called "draw". Then mutate() and use map_lgl() to
# show TRUE if any values in draw are face cards (J, Q, K) and FALSE otherwise

hands <- tibble(draw = map(rep(5, 100), ~ draw_card(., report = "value"))) %>% 
  mutate(face = map_lgl(draw, ~ ifelse(any(c("J", "Q", "K") %in% .),
                                       TRUE,
                                       FALSE)))

# Slicing the first 5 rows of the hands tibble, passing it through gt() for
# formatting and adding a title, subtitle, and column labels

hands %>% 
  slice(1:5) %>% 
  gt() %>% 
  tab_header(title = "Hands of Five Cards",
             subtitle = "Checking for Face Values") %>% 
  cols_label(draw = "Draw",
             face = "Face Cards?")

```

#### 1c)

```{r question_1c, echo=FALSE}

# This r chunk draws a hand of 12 cards and prints their names and points in a
# nice gt table

# Creating a tibble called draw_12 which saves the names of 12 cards drawn
# randomly from the deck after the seed was set to 4

set.seed(4)
draw_12 <- tibble(card = draw_card(12, report = "name"))

# Resetting the seed to 4 and using the magrittr assignment pipe operator to add
# a new column to draw_12, showing the points for each of the 12 cards. Using
# the draw_card() function without resetting the seed to 4 would result in a
# random draw of 12 cards, whose point values would be unlikely to match the
# names I got when creating draw_12; but by setting the seed again, I guarantee
# the same cards will be drawn, so the point values will match up

set.seed(4)
draw_12 %<>% 
  mutate(points = draw_card(12, report = "points"))

# Passing the modified draw_12 tibble through gt() and adding a title and column
# labels

draw_12 %>% 
  gt() %>% 
  tab_header(title = "Hand of 12 Cards") %>% 
  cols_label(card = "Card",
             points = "Points")

```

#### 1d)

```{r question_1d, echo=FALSE}

# This r chunk finds the mean point value for the deck of cards and assigns it
# to an object to insert in the mad lib. Rounding to 3 digits was pretty
# arbitrary, but modeled after the display in the pset plots which showed a mean
# of 7.231

deck_mean <- draw_card(52, report = "points") %>% 
  mean() %>% 
  round(digits = 3)

```

The mean number of points in our entire deck is **`r deck_mean`**.

#### 1e)

The mean of the bootstrapped resamples is different from the original sample mean because bootstrapping introduces sampling variation - the mean of each of the 1000 resamples is likely to be different than the mean of the original sample (because it's unlikely we'll draw all 12 of the original cards while sampling with replacement) and though the mean of those means should be *close* to the original mean, it's unlikely to be identical.

```{r question_1e, echo=FALSE}

# This r chunk sets the seed to 5 and creates a distribution of bootstrapped
# resamples from the hand of 12 cards (draw_12) and uses it to replicate the
# plot in the question prompt

# I decided not to use a map function here because using rep_sample_n to create
# the bootstrap distribution was so straightforward. I first took 1000 samples
# (with replacement) of size 12 from draw_12, grouped by replicate, and
# summarized the mean of points for each replicate, calling the resulting tibble
# bootstrap

set.seed(5)
bootstrap <- rep_sample_n(draw_12, size = 12, reps = 1000, replace = TRUE) %>% 
  group_by(replicate) %>% 
  summarize(mean_points = mean(points))

# I then diverted for a moment to take the mean of the original sample (draw_12)
# and assign it to an object so I could easily use it to add a vertical line to
# the plot below

sample_mean <- draw_12 %>% 
  summarize(mean(points)) %>% 
  pull()

# I then branched off that diversion into another similar one, taking the mean
# of the bootstrap distribution and saving it to an object to be easily inserted
# into the plot below

bootstrap_mean <- bootstrap %>% 
  pull(mean_points) %>% 
  mean()

# I then used the bootstrap distribution to plot a histogram showing the
# distribution of means across the 1,000 replications

bootstrap %>% 
  ggplot(aes(mean_points)) +
  
# setting bin number to match plot in question prompt  
  
  geom_histogram(bins = 20) +
  
# theme_classic for easy formatting of a clean display
  
  theme_classic() +
  
# adding title, subtitle, and nice-looking axis titles
  
  labs(title = "Distribution of 1000 Bootstrapped Resamples",
       subtitle = "From original 12 card sample with mean 7.167",
       x = "Points",
       y = "Samples") +
  
# adding vertical line at the location of the sample mean, then adding text in a
# matching color to describe the meaning of the line
  
  geom_vline(xintercept = sample_mean, color = "pink") +
  geom_text(x = 7.05,
            y = 50,
            label = "Original Sample Mean",
            color = "pink",
            angle = 90) +  
  
# adding vertical line at the location of the bootstrap mean, then adding text
# in a matching color to describe it
  
  geom_vline(xintercept = bootstrap_mean, color = "light blue") +
  geom_text(x = 7.3,
            y = 52,
            label = "Mean of Bootstraped Samples",
            color = "light blue",
            angle = 90)

```

#### 1f)

```{r question_1f, echo=FALSE}

# This r chunk creates confidence intervals from the bootstrapped resample
# distribution and shows the intervals for each level in a gt table

# Decided first to define a function with level as a parameter to report the
# intervals, knowing I'd need to use essentially the same code four different
# times to make CIs at each of four different confidence intervals. I took the
# lower_prob and upper_prob definitions from ch. 10 of PPBDS. I split up the
# lower and upper bounds of the intervals into different columns so I could
# easily subtract lower from upper or otherwise modify them if necessary

make_intervals <- function(level){
  lower_prob <- (1 - level) / 2
  upper_prob <- level + lower_prob
  bootstrap %>% 
    summarize(level = level,
              lower = quantile(mean_points, lower_prob),
              upper = quantile(mean_points, upper_prob))
}

# I then called on that function four times, at each of the levels specified, to
# create four dataframes, each one with three variables: level, lower bound, and
# upper bound

ci_80 <- make_intervals(.8)
ci_90 <- make_intervals(.9)
ci_95 <- make_intervals(.95)
ci_99 <- make_intervals(.99)

# I then combined those four dataframes into one

intervals <- bind_rows(ci_80, ci_90, ci_95, ci_99)

# I then added a column combining the lower and upper bounds to display them as
# an interval by using my new friend the paste() function. I think it's probably
# an unconventional use, but it's purely for aesthetics in the gt table below. I
# had worked up to this point before seeing the updated Pset 6A, and the
# original Pset 6 didn't have a model table to replicate, so I initially had
# this formatted differently; it was easier to use paste() to make the table
# look the same than to reconfigure my code to actually produce the interval as
# output from the make_interval function

intervals$interval <- paste(
  "(",
  round(intervals$lower, digits = 1),
  ", ",
  round(intervals$upper, digits = 1),
  ")",
  sep = "")

# Selecting the level and interval columns and using mutate() and
# paste() to change the formatting of level so it looks a little nicer in the gt
# table

intervals %>% 
  select(level, interval) %>%  
  mutate(level = paste(level * 100, "%", sep = "")) %>%
  
# Table time! Passing the above through gt() and adding a title and subtitle,
# along with column labels (bolded using md() for a nicer appearance), column
# formatting (I think it looks better with both columns aligned along the edges
# rather than centered; level defaults to left alignment, but I had to
# explicitly set the alignment of interval to "right"), and a source note. It's
# not a perfect replication of the table in the question prompt, and the reason
# for that is that I think what I've done looks better
  
  gt() %>% 
  tab_header(title = "Confidence Intervals for Average Point Value",
             subtitle = "Bootstrapped Resamples on a 12 Card Hand") %>% 
  cols_label(level = md("**Level**"),
             interval = md("**Interval**")) %>% 
  cols_align(align = "right",
             columns = vars(interval)) %>% 
  tab_source_note(source_note = 
                    "Original Sample Mean: 7.167")

```

#### 1g)

```{r question_1g, echo=FALSE}

# This r chunk writes the function width_ci to take a sample of n cards and
# produce the CI at a specified level. It uses that function to make a tibble
# with sample sizes 2:52 and confidence levels .9, .95, and .99. It then plots
# the resulting tibble to show how CIs differ based on sample size and
# confidence level

# Setting the seed as instructed

set.seed(6)

# This function borrows heavily from the make_intervals function introduced in
# 1f. The use of level, including lower_prob and upper_prob assignments, is
# exactly the same, and the process of using rep_sample_n, group_by(replicate),
# and summarize() to get the mean points in each replicate is also identical.
# The big differences are that 1) instead of using the bootstrap dataframe as
# the tbl argument of rep_sample_n, this uses a sampling of size n from
# create_deck(); 2) instead of having the function produce the upper and lower
# bounds of the interval, I subtract lower from upper and pull() the result so
# the function outputs just the width of the interval

width_ci <- function(n, level){
  lower_prob <- (1 - level) / 2
  upper_prob <- level + lower_prob
  sample_n(create_deck(), size = n) %>% 
    rep_sample_n(size = n, reps = 1000, replace = TRUE) %>% 
    group_by(replicate) %>%   
    summarize(mean_points = mean(points)) %>% 
    summarize(level = level,
              lower = quantile(mean_points, lower_prob),
              upper = quantile(mean_points, upper_prob)) %>% 
    summarize(width = upper - lower) %>% 
    pull(width)
}

# Making a tibble of sample sizes

widths <- tibble(size_n = 2:52)

# Mutating the widths tibble to add three new variables, each of which saves the
# CI widths at a given level. It took me a long time to figure out how to do
# this, because I couldn't figure out how to pass multiple parameters through
# width_ci using a map function (using n = . to pass the size_n values through
# to the width_ci() function and manually setting the level was what finally
# worked!). It was pretty frustrating for a while, but we got there in the end.

widths %<>% 
  mutate(width_90 = map_dbl(size_n, ~ width_ci(n = ., level = .9)),
         width_95 = map_dbl(size_n, ~ width_ci(n = ., level = .95)),
         width_99 = map_dbl(size_n, ~ width_ci(n = ., level = .99)))

# Using pivot_longer to modify widths, giving me one column with all the sample
# sizes (each repeated three times, another with the confidence level, and
# another with the width of the CI)

widths %<>% 
  pivot_longer(cols = width_90:width_99,
               names_to = "confidence_level",
               values_to = "ci_width")

# It was simple enough at that point to create this plot, putting sample size on
# the x axis, ci_width on the y axis, and mapping confidence level by color.
# Used geom_point() to get the scatterplot and theme_classic() for its nice
# clean look

widths %>% 
  ggplot(aes(size_n, ci_width, color = confidence_level)) +
  geom_point() +
  theme_classic() +
  
# Adding title, subtitle, and axis labels, replicating text from the plot.
# Formatting of title = "" is a bit wonky to prevent it from going past 80
# characters on a single line
  
  labs(title = 
        "Width of Bootstrapped Confidence Intervals for Different Sample Sizes",
       subtitle = "Calculating the Mean Point Value from a Deck of Cards",
       x = "Sample Size",
       y = "Width of Confidence Interval \n (Percentile Method)") +
  
# Adding a legend title and changing the displayed names of the confidence
# levels
  
  scale_color_discrete(name="Confidence Level",
                         breaks=c("width_90", "width_95", "width_99"),
                         labels=c("90%", "95%", "99%"))

```

## Question 2: Shiny

```{r question_2, echo=FALSE}

# This r chunk saves the plot from 1g) to the shiny directory, specifying width
# and height within ggsave() to get rid of the message output it otherwise gives
# ("Saving 7 X 5 in image")

ggsave("ps_6_shiny/dist_plot.png",
       width = 7,
       height = 5)

```

View the plot from 1g) in my published Shiny app at https://wkcook.shinyapps.io/ps_6_shiny/

### Worked With: None
Received a little help on 1g) from Dillon Smith at his Study Hall on 3/25
