---
title: "Problem Set 6"
author: "Westley Cook"
date: "3/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# standard first load

library(tidyverse)

# loading for tables in question 1

library(gt)

# loading to use assignment pipe operator in 1c

library(magrittr)

# loading to use rep_sample_n for 1e

library(infer)

```

## Question 1: Sampling and Confidence Intervals

```{r question_1_setup, echo=FALSE}

create_deck <- function(){
tibble(value = c(rep(c(as.character(2:10), "J", "Q", "K", "A"), 4)),
       points = rep(c(2:10, rep(10, 4)), 4),
       suit = c(rep("diamonds", 13),
                rep("hearts", 13),
                rep("clubs", 13),
                rep("spades", 13)),
       name = paste(value, suit, sep = " of "))
}

draw_card <- function(n, report = c("suit", "value", "points", "name")){
  stopifnot(is.numeric(n))
  create_deck() %>% 
  pull(report) %>% 
  sample(n)
}

```

#### 1a)

A call of my draw_card() function with n = 4 and report = "name" produces the following output:

```{r question_1a, echo=FALSE}

# what does print a call mean?

set.seed(2)
draw_card(4, report = "name")

```

#### 1b)

```{r question_1b, echo=FALSE}

set.seed(3)

hands <- tibble(draw = map(rep(5, 100), ~ draw_card(5, report = "value"))) %>% 
  mutate(face = map_lgl(draw, ~ ifelse(any(. %in% c("J", "Q", "K")),
                                       TRUE,
                                       FALSE)))

hands %>% 
  slice(1:5) %>% 
  gt() %>% 
  tab_header(title = "Hands of Five Cards",
             subtitle = "Checking for Face Values") %>% 
  cols_label(draw = "Draw",
             face = "Face Cards?")

```

#### 1c)

```{r question_1c, echo=FALSE}

set.seed(4)
draw_12 <- tibble(card = draw_card(12, report = "name"))

set.seed(4)
draw_12 %<>% 
  mutate(points = draw_card(12, report = "points"))

draw_12 %>% 
  gt() %>% 
  tab_header(title = "Hand of 12 Cards") %>% 
  cols_label(card = "Card",
             points = "Points")

```

#### 1d)

```{r question_1d, echo=FALSE}

deck_mean <- draw_card(52, report = "points") %>% 
  mean() %>% 
  round(digits = 3)

```

The mean number of points in our entire deck is **`r deck_mean`**.

#### 1e)

The mean of the bootstrapped resamples is different from the original sample mean because bootstrapping introduces sampling variation - the mean of each of the 1000 resamples is likely to be different than the mean of the original sample (because it's unlikely we'll draw all 12 of the original cards while sampling with replacement) and though the mean of those means should be *close* to the original mean, it's unlikely to be identical.

```{r question_1e, echo=FALSE}

set.seed(5)
bootstrap <- rep_sample_n(draw_12, size = 12, reps = 1000, replace = TRUE) %>% 
  group_by(replicate) %>% 
  summarize(mean_points = mean(points))

sample_mean <- draw_12 %>% 
  summarize(mean(points)) %>% 
  pull()

bootstrap_mean <- bootstrap %>% 
  pull(mean_points) %>% 
  mean()

bootstrap %>% 
  ggplot(aes(mean_points)) +
  geom_histogram(bins = 20) +
  theme_classic() +
  labs(title = "Distribution of 1000 Bootstrapped Resamples",
       subtitle = "From original 12 card sample with mean 7.167",
       x = "Points",
       y = "Samples") +
  geom_vline(xintercept = sample_mean, color = "pink") +
  geom_text(x = 7.05,
            y = 50,
            label = "Original Sample Mean",
            color = "pink",
            angle = 90) +  
  geom_vline(xintercept = bootstrap_mean, color = "light blue") +
  geom_text(x = 7.3,
            y = 52,
            label = "Mean of Bootstraped Samples",
            color = "light blue",
            angle = 90)

```

#### 1f)

```{r question_1f, echo=FALSE}

make_intervals <- function(level){
  lower_prob <- (1 - level) / 2
  upper_prob <- level + lower_prob
  bootstrap %>% 
    summarize(level = level,
              lower = quantile(mean_points, lower_prob),
              upper = quantile(mean_points, upper_prob))
}

ci_80 <- make_intervals(.8)
ci_90 <- make_intervals(.9)
ci_95 <- make_intervals(.95)
ci_99 <- make_intervals(.99)

intervals <- bind_rows(ci_80, ci_90, ci_95, ci_99)

# explain why you formatted it this way instead of in tuples

intervals$interval <- paste(
  round(intervals$lower, digits = 2),
  round(intervals$upper, digits = 2),
  sep = " to ")

intervals %>% 
  select(level, interval) %>%  
  mutate(level = paste(level * 100, "%", sep = "")) %>%
  gt() %>% 
  tab_header(title = "Confidence Intervals for Average Point Value",
             subtitle = "Bootstrapped Resamples on a 12 Card Hand") %>% 
  cols_label(level = md("**Level**"),
             interval = md("**Interval**")) %>% 
  cols_align(align = "right",
             columns = vars(interval)) %>% 
  tab_source_note(source_note = 
                    "Original Sample Mean of 7.167")

```

#### 1g)

```{r question_1g, echo=FALSE}

set.seed(6)

width_ci <- function(n, level){
  lower_prob <- (1 - level) / 2
  upper_prob <- level + lower_prob
  sample_n(create_deck(), size = n) %>% 
    rep_sample_n(size = n, reps = 1000, replace = TRUE) %>% 
    group_by(replicate) %>%   
    summarize(mean_points = mean(points)) %>% 
    summarize(level = level,
              lower = quantile(mean_points, lower_prob),
              upper = quantile(mean_points, upper_prob)) %>% 
    summarize(width = upper - lower) %>% 
    pull(width)
}

widths_1 <- tibble(size_n = 2:52)

widths_1 %<>% 
  mutate(width_90 = map_dbl(size_n, ~ width_ci(n = ., level = .9)),
         width_95 = map_dbl(size_n, ~ width_ci(n = ., level = .95)),
         width_99 = map_dbl(size_n, ~ width_ci(n = ., level = .99)))

widths_1 %<>% 
  pivot_longer(cols = width_90:width_99,
               names_to = "confidence_level",
               values_to = "ci_width")

widths_1 %>% 
  ggplot(aes(size_n, ci_width, color = confidence_level)) +
  geom_point() +
  theme_classic() +
  labs(title = "Width of Bootstrapped Confidence Intervals for Different Sample Sizes",
       subtitle = "Calculating the Mean Point Value from a Deck of Cards",
       x = "Sample Size",
       y = "Width of Confidence Interval \n (Percentile Method)") +
  scale_color_discrete(name="Confidence Level",
                         breaks=c("width_90", "width_95", "width_99"),
                         labels=c("90%", "95%", "99%"))

```

## Question 2: Shiny

##### View the plot from 1g) in my published Shiny app at https://wkcook.shinyapps.io/ps_6_shiny/

```{r question_2, echo=FALSE}

# Specifying width and height to get rid of message output "Saving 7 X 5 in
# image"

ggsave("ps_6_shiny/dist_plot.png",
       width = 7,
       height = 5)

```

### Worked With: None
Received a little help on 1g) from Dillon Smith at his Study Hall on 3/25
